---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DMS

**Title**: Adaptive changepoint inference in high dimension

**Description**: Implements the double-max-sum (DMS) method for adaptive changepoint inference in high dimension, as proposed by [Wang and Feng (2023)](https://doi.org/10.1093/jrsssb/qkad048). Additionally, it offers various other adaptive testing approaches, including [Liu, Zhang, Zhang and Liu (2020)](https://doi.org/10.1111/rssb.12375) and [Zhang, Wang and Shao (2022)](https://doi.org/10.1080/01621459.2021.1884562), as well as non-adaptive ones, such as [Jirak (2015)](https://doi.org/10.1214/15-AOS1347), [Yu and Chen (2021)](https://doi.org/10.1111/rssb.12406), and [Wang, Zou, Wang and Yin (2019)](https://doi.org/10.1142/S201032631950014X).

## Installation

You can install the development version of DMS from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ghwang-nk/DMS")
```

## Getting started

```{r example}
library(DMS)
?DMS
?LZZL20
?ZWS22
?J15
?max_2sample
?YC21
?WZWY19
```

## References

- Jirak, M. (2015) Uniform change point tests in high dimension. The Annals of Statistics, 43, 2451–2483.
- Liu, B., Zhou, C., Zhang, X. and Liu, Y. (2020) A Unified Data-Adaptive Framework for High Dimensional Change Point Detection. Journal of the Royal Statistical Society Series B: Statistical Methodology, 82, 933–963.
- Wang, G. and Feng, L. (2023) Computationally efficient and data-adaptive changepoint inference in high dimension. Journal of the Royal Statistical Society Series B: Statistical Methodology, 85, 936–958.
- Wang, Y., Zou, C., Wang, Z. and Yin, G. (2019) Multiple change-points detection in high dimension. Random Matrices: Theory and Applications, 08, 1950014.
- Yu, M. and Chen, X. (2021) Finite Sample Change Point Inference and Identification for High-Dimensional Mean Vectors. Journal of the Royal Statistical Society Series B: Statistical Methodology, 83, 247–270.
- Zhang, Y., Wang, R. and Shao, X. (2022) Adaptive Inference for Change Points in High-Dimensional Data. Journal of the American Statistical Association, 117, 1751–1762.

## Acknowledgments

We would like to express our sincere gratitude to [Professor Xiaofeng Shao](http://publish.illinois.edu/xshao/) for his invaluable assistance in helping us implement the ZWS22 test, as introduced by [Zhang, Wang and Shao (2022)](https://doi.org/10.1080/01621459.2021.1884562). The core implementation of the test is based on an adapted version of their Matlab code. For those interested, the original Matlab code can be accessed through this link: <https://doi.org/10.1080/01621459.2021.1884562>.
